---
title: "Deutsch Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    self_contained: false
---
<style>                     
.navbar {
  background-color:rgb(255, 140, 0);
  border-color:white;
}
.inner {
  background-color:rgb(255, 140, 0);
  border-color:white;
}

.navbar-brand {
color:white!important;
}
</style>  

```{r setup, include=FALSE}
library(flexdashboard)

goal_sentences <- 3500
goal_sentences_2022 <- 240
```

# Entrada

## Columna {data-width=600 .tabset}

### Semanal

```{r, fig.width=8}
bar_dias
```

### Mensual

```{r, fig.width=8}
bar_meses
```

## Columna {data-width=400}

### Oraciones en Anki

```{r, fig.width = 10, fig.height=5}
gauge(sum(Anki),
      0,
      goal_sentences, 
      abbreviateDecimals = 2,
      label = "Oraciones Totales",
      gaugeSectors(
  success = c(goal_sentences*0.8, goal_sentences),
  warning = c(goal_sentences*0.5, goal_sentences*.8 - 1),
  danger = c(0, goal_sentences*0.5 - 1)))
```


### Oraciones agregadas en 2022
```{r, fig.width = 10, fig.height=5}
gauge(Anki[3],
      0,
      goal_sentences_2022,
      abbreviateDecimals = 2,
      label = "Oraciones Nuevas",
      gaugeSectors(
  success = c(goal_sentences_2022*0.8, goal_sentences_2022),
  warning = c(goal_sentences_2022*0.5, goal_sentences_2022*0.8 - 1),
  danger = c(0, goal_sentences_2022*0.5 - 1)))
```

# Vista Anual

## Columna {data-height=850 .tabset}

### 2020
```{r, fig.width=9, fig.height=4}
bar_meses_2020
```

### 2021
```{r, fig.width=9, fig.height=4}
bar_meses_2021
```

### 2022
```{r, fig.width=9, fig.height=4}
bar_meses_2022
```

## Columna {data-height=100}

### Total Horas 2020
```{r}
valueBox(Immersion[1], icon = "fa-clock")
```

### Total Horas 2021
```{r}
valueBox(Immersion[2], icon = "fa-clock")
```

### Total Horas 2022
```{r}
valueBox(Immersion[3], icon = "fa-clock")
```

## Columna {data-height=100}

### Oraciones Nuevas 2020
```{r}
valueBox(Anki[1], icon = "fa-folder")
```

### Oraciones Nuevas 2021
```{r}
valueBox(Anki[2], icon = "fa-folder")
```

### Oraciones Nuevas 2022
```{r}
valueBox(Anki[3], icon = "fa-folder")
```
